Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-12 paper/paper.tex
added nauty reference

Some other forms do not translate. For example, another invariant which can be effective on regular
graphs is to count the number of neighbours of a vertex which are present in a triangle. Removing a
single vertex can alter this count arbitrarily, so we cannot make use of this fact.

>>>>

Some other forms do not translate. For example, another invariant which can be effective on regular
graphs is to count the number of neighbours of a vertex which are present in a triangle \cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot make use of this fact.
